Solving Combinatorial Puzzles with Parallel Evolutionary Algorithms \thanks{This work was supported by a private funding of Velbazhd Software LLC.}

### 2019-03-07 Solving-Combinatorial-Puzzles-with-Parallel-Evolutionary-Algorithms/paper.tex
Some changes were done by Vera Angelova.

Solutions of a particular problem are represented as vectors of values into the solution space. All selected solution vectors are the population of the algorithm. The most common way of initial population establishment is by generation of random vectors. Each new generation appears in the population after recombination of selected individuals. In genetic algorithms recombination is done by two consequent operators - crossover and mutation. Which individuals to participate in the recombination process is decided by application of selection operator. It is very common during selection process elitism rule to be applied. Elitism means that some percent of the best found solutions survive to the real end of the optimization process. Because such optimization procedure as implemented in the genetic algorithms is iterative, stopping criteria is needed. The most used stopping criteria is initially given number of genetic algorithm generations.

Genetic algorithms are the base of the genetic programming which is used in this research. Each element of the solution vector actually is an operation applied over the state of the Rubik's cube. Ordered set of such instructions is actually an algorithmic program. Because there is no direct intermediate relation between the individuals in a particular population genetic algorithms are highly appropriate for implementation in parallel computing or distributed computing. Population of the genetic algorithm can be easily divided is many sub-population and it can be distributed on many processors/cores or even heterogeneous computers in a cluster. Separation of the global population is the preferred approach, but in cases where only the fitness value calculation is time consuming, population is kept in the central processor/computer and only fitness value calculation is sent to the other contributing processors/computers.

@@

Data structures are on first side of the modeling. On the second side are the algorithmic operations done over the data structures. The cube has six sides that is why the minimum number of operations over the cube is six. Six capital letters are used for 90 degrees clockwise rotations, as proposed in \cite{randall01,balabanov02}: \\ 
\\
T (Top) –90 degrees clockwise rotation of the top side; \\ 
L (Left) –90 degrees clockwise rotation of the left side; \\ 
B (Back) –90 degrees clockwise rotation of the back side; \\ 
R (Right) –90 degrees clockwise rotation of the right side; \\ 
F (Front) –90 degrees clockwise rotation of the front side; \\ 
D (Down) –90 degrees clockwise rotation of the down side. \\

@@

With this clear idea for a formal Rubik's cube grammar it is neutral genetic algorithm individuals to be represented as formal grammar sentences with variable length. Each of the letters can appear at any position many times repeated in the chromosome. As it was appointed in \cite{korf01} the average expected length of the chromosomes can be between 50 and 100.

>>>>

Solutions of a particular problem are represented as vectors of values into the solution space. All selected solution vectors are the population of the algorithm. The most common way of initial population establishment is by generation of random vectors. Each new generation appears in the population after recombination of selected individuals. In genetic algorithms recombination is done by two consequent operators - crossover and mutation. Which individuals to participate in the recombination process is decided by application of selection operator. It is very common during selection process elitism rule to be applied. Elitism means that some percent of the best found solutions survive to the real end of the optimization process. Because genetic algorithms based optimization is an iterative optimization a stopping criteria is needed. The most used stopping criteria is initially given number of genetic algorithm generations.

Genetic algorithms are the base of the genetic programming which is used in this research. Each element of the solution vector actually is an operation applied over the state of the Rubik's cube. Ordered set of such instructions is actually an algorithmic program. Because there is no direct intermediate relation between the individuals in a particular population genetic algorithms are highly appropriate for implementation in parallel computing or distributed computing. Population of the genetic algorithm can be easily divided in many sub-population and it can be distributed on many processors/cores or even heterogeneous computers in a cluster. Separation of the global population is the preferred approach, but in cases where only the fitness value calculation is time consuming, population is kept in the central processor/computer and only fitness value calculation is sent to the other contributing processors/computers.

@@

Data structures are the first side of the modeling proccess. On the second side are the algorithmic operations done over the data structures. The cube has six sides that is why the minimum number of operations over the cube is six. Six capital letters are used for 90 degrees clockwise rotations, as proposed in \cite{randall01,balabanov02}: \\ 
\\
T (Top) –90 degrees clockwise rotation of the top side; \\ 
L (Left) –90 degrees clockwise rotation of the left side; \\ 
B (Back) –90 degrees clockwise rotation of the back side; \\ 
R (Right) –90 degrees clockwise rotation of the right side; \\ 
F (Front) –90 degrees clockwise rotation of the front side; \\ 
D (Down) –90 degrees clockwise rotation of the down side. \\

@@

With the presented ideas for a formal Rubik's cube grammar the neutral choice is genetic algorithm individuals to be represented as formal grammar sentences with variable length. Each of the letters can appear at any position many times repeated in the chromosome. As it was appointed in \cite{korf01} the average expected length of the chromosomes can be between 50 and 100.
